---
title: A University of Warwick Themed Presentation
subtitle: TODO - maybe add Warwick logo to title page?
author: Your Name
date: last-modified
date-format: long
format: 
  warwickpres-revealjs: default
---

## Introduction

This is a Quarto presentation format that is consistent with The University of Warwick's [ID7 branding](https://id7.warwick.ac.uk) (especially [colours](https://id7.warwick.ac.uk/components/colour-palette/) and [font](https://warwick.ac.uk/services/its/servicessupport/web/sitebuilder2/id7/faqs/fonts/)).

:::{.callout-note}
It is *not*, however, a University of Warwick branded presentation in the sense that it does not feature the university logo, nor has it been officially signed-off by whoever would need to sign-off such things.
:::

:::{.notes}
Speaker notes go here.
:::

# inverse class for section headings {.inverse}

## inverse class is also useful for stressing *key points*. {.inverse .center-h .center .larger125}

## Colours

There's a colour for inline code such as `x <- c(1, 3, 6)` and `{.inverse}`.

There's also a colour for short [links](https://github.com/Warwick-Stats-Resources/warwickpres) and full ones like <https://quarto.org/docs/presentations/revealjs/>.

## Colours {.inverse}

There's a colour for inline code such as `x <- c(1, 3, 6)` and `{.inverse}`.

There's also a colour for short [links](https://github.com/Warwick-Stats-Resources/warwickpres) and full ones like <https://quarto.org/docs/presentations/revealjs/>.

- The inline code and link colours change when the inverse class is applied.
- I wouldn't recommend using inverse class for a slide with this much text though.


## Code

The extension includes a custom syntax highlighting theme:

```{r}
#| echo: true
#| eval: false
library(dplyr)
library(palmerpenguins)

penguins %>%
  mutate(
    long_flipper = case_when(
      species == "Adelie" & flipper_length_mm > 195 ~ TRUE,
      species == "Chinstrap" & flipper_length_mm > 200 ~ TRUE,
      species == "Gentoo" & flipper_length_mm > 225 ~ TRUE,
      TRUE ~ FALSE
    )
  ) %>%
  mutate(
    body_mass_kg = body_mass_g / 1000,
    bill_length_cm = bill_length_mm / 10,
    bill_depth_cm = bill_depth_mm / 10
  )
```

## warwickplots

TODO: expand on the link between the theme and {warwickplots}, once finished (include adding `theme_warwick()`, giving link to warwickplots repo). Also, split out code and output (tabset?) on this slide.

```{r}
library(warwickplots)
library(ggplot2)
ggplot(diamonds[sample(nrow(diamonds), 1000), ], aes(carat, price)) +
  geom_point(aes(colour = clarity)) +
  scale_colour_palette_d(warwick_palettes$aubergine) +
  labs(title = "A plot with a Warwick palette and theme") #+
  # theme_warwick()
```

## Callouts {.smaller70}

There are custom colours for callouts: 

:::{.callout-note}
A note
:::

:::{.callout-warning}
A warning
:::

:::{.callout-important}
Something important
:::

:::{.callout-tip}
This is a good idea
:::

:::{.callout-caution}
Be careful about doing this
:::

These require a raw html chunk at the end of the presentation .qmd file (included in template).

# Non-Warwick-specific nice-to-haves {.inverse}

## Alignment

There are classes to help with text alignment:

:::{.center-h}
`{.center-h}` gives horizontally-centered text
:::

:::{.right}
`{.right}` gives right-aligned text
:::

:::{.callout-note}
For all revealjs Quarto presentations, applying `{.center}` to the slide title vertically centers the whole slide.
:::

## Sizing

There are classes to help size text by a given percentage:

[`{.smaller90}`]{.smaller90}, [`{.smaller80}`]{.smaller80}, [`{.smaller75}`]{.smaller75}
[`{.smaller70}`]{.smaller70}, [`{.smaller60}`]{.smaller60}, [`{.smaller50}`]{.smaller50}

[`{.larger125}`]{.larger125}, [`{.larger150}`]{.larger150}, [`{.larger175}`]{.larger175}, 
[`{.larger200}`]{.larger200}, [`{.larger250}`]{.larger250}

## TODO

- Maybe take some ideas from? [kakashi](https://github.com/malcolmbarrett/kakashi-quarto-theme) theme

## More Information

You can learn more about controlling the appearance of RevealJS output here: <https://quarto.org/docs/presentations/revealjs/>

## How to edit the theme/see available classes

```{=html}
<!-- needs to be last chunk of presentation otherwise creates an extra slide -->
<!-- requires Quarto v1.3 -->
<!-- tint80 for border, tint20 for title -->
<!-- this should hopefully no longer be necessary in Quarto 1.4 -->
<!-- https://github.com/quarto-dev/quarto-cli/issues/5038 -->
<style type="text/css">
div.callout-note {
  border-left-color: #265D8E !important;
}

div.callout-note.callout-style-default .callout-title {
  background-color: #D9E2EB !important;
}

div.callout-caution {
  border-left-color: #A93634 !important;
}

div.callout-caution.callout-style-default .callout-title {
  background-color: #F0DCDB !important;
}

div.callout-tip {
  border-left-color: #335D27 !important;
}

div.callout-tip.callout-style-default .callout-title {
  background-color: #DBE2D9 !important;
}

div.callout-important {
  border-left-color: #6F4D7A !important;
}

div.callout-important.callout-style-default .callout-title {
  background-color: #E6E0E7 !important;
}

div.callout-warning {
  border-left-color: #8E5826 !important;
}

div.callout-warning.callout-style-default .callout-title {
  background-color: #EBE1D9 !important;
}
</style>
```

