---
title: A University of Warwick Themed Presentation
author: Your Name
date: last-modified
date-format: long
format: 
  warwickpres-revealjs: default
#theme: [default, _extensions/warwickpres/custom.scss]
echo: true
---

## Introduction

This is a Quarto presentation format that is consistent with The University of Warwick's [ID7 branding](https://id7.warwick.ac.uk) (especially [colours](https://id7.warwick.ac.uk/components/colour-palette/) and [font](https://warwick.ac.uk/services/its/servicessupport/web/sitebuilder2/id7/faqs/fonts/)).

:::{.callout-note}
It is *not*, however, a University of Warwick branded presentation in the sense that it does not feature the university logo, nor has it been officially signed-off by whoever would need to sign-off such things.
:::


# inverse class for section headings {.inverse}

## Colours

There's a colour for inline code such as `x <- c(1, 3, 6)` and `{.inverse}`.

There's also a colour for short [links](https://github.com/Warwick-Stats-Resources/warwickpres) and full ones like <https://quarto.org/docs/presentations/revealjs/>.

## Colours {.inverse}

There's a colour for inline code such as `x <- c(1, 3, 6)` and `{.inverse}`.

There's also a colour for short [links](https://github.com/Warwick-Stats-Resources/warwickpres) and full ones like <https://quarto.org/docs/presentations/revealjs/>.

- The inline code and link colours change when the inverse class is applied.


## inverse class is also useful for stressing key points {.inverse .center-h .center}

## Code

The extension includes a custom syntax highlighting theme:

```{r}
#| eval: false
library(dplyr)
library(palmerpenguins)

penguins %>%
  mutate(
    long_flipper = case_when(
      species == "Adelie" & flipper_length_mm > 195 ~ TRUE,
      species == "Chinstrap" & flipper_length_mm > 200 ~ TRUE,
      species == "Gentoo" & flipper_length_mm > 225 ~ TRUE,
      TRUE ~ FALSE
    )
  ) %>%
  mutate(
    body_mass_kg = body_mass_g / 1000,
    bill_length_cm = bill_length_mm / 10,
    bill_depth_cm = bill_depth_mm / 10
  )
```

## warwickplots

TODO: expand on the link between the theme and {warwickplots}, once finished (include adding `theme_warwick()`, giving link to warwickplots repo). Also, split out code and output (tabset?) on this slide.

```{r}
library(warwickplots)
library(ggplot2)
ggplot(diamonds[sample(nrow(diamonds), 1000), ], aes(carat, price)) +
  geom_point(aes(colour = clarity)) +
  scale_colour_palette_d(warwick_palettes$aubergine) +
  labs(title = "A plot with a Warwick palette and theme") #+
  # theme_warwick()
```


## Where to edit the theme/see available classes

## Callouts {.smaller70}

TODO: Figure out how to change colours on the callouts. See [discussion](https://github.com/quarto-dev/quarto-cli/discussions/4755).

:::{.callout-note}
A note
:::

:::{.callout-warning}
A warning
:::

:::{.callout-important}
Something important
:::

:::{.callout-tip}
This is a good idea
:::

:::{.callout-caution}
Be careful about doing this
:::

# Non-Warwick-specific nice-to-haves {.inverse}

## Alignment

There are classes to help with text alignment:

:::{.center-h}
`{.center-h}` gives horizontally-centered text
:::

:::{.right}
`{.right}` gives right-aligned text
:::

:::{.callout-note}
For all revealjs Quarto presentations, applying `{.center}` to the slide title vertically centers the whole slide.
:::

## Sizing

There are classes to help size text by a given percentage:

[`{.smaller90}`]{.smaller90}, [`{.smaller80}`]{.smaller80}, [`{.smaller75}`]{.smaller75}
[`{.smaller70}`]{.smaller70}, [`{.smaller60}`]{.smaller60}, [`{.smaller50}`]{.smaller50}

[`{.larger125}`]{.larger125}, [`{.larger150}`]{.larger150}, [`{.larger175}`]{.larger175}, 
[`{.larger200}`]{.larger200}, [`{.larger250}`]{.larger250}

## More Information

You can learn more about controlling the appearance of RevealJS output here: <https://quarto.org/docs/presentations/revealjs/>
